% arara: xelatex
% arara: xelatex
% arara: xelatex
\documentclass[thesis=M,english,hidelinks]{template/FITthesis}[2019/12/23]
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}

\usepackage{gensymb}
\usepackage{pdfpages}
\usepackage{dirtree}
\usepackage{multirow}

\DeclareUnicodeCharacter{2009}{ }
\DeclareUnicodeCharacter{200B}{ }
\linespread{1.1}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

\setlrmarginsandblock{3.5cm}{3cm}{*}
\setulmarginsandblock{3cm}{*}{1}
\checkandfixthelayout 

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
% EDIT THIS
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 

\department{Department of Software Engineering}
\title{Surrounding Environment Effects in Virtual Reality}
\authorGN{Marián} 
\authorFN{Hlaváč} 
\author{Marián Hlaváč}
\authorWithDegrees{Bc. Marián Hlaváč}
\supervisor{Ing. Jiří Chludil}
\acknowledgements{I want to thank all testers, who accepted my invitation and participated 
	in the user testing, despite the difficult current pandemic situation.

	My thesis supervisor Ing. Jiří Chludil is also owed many thanks, 
	as he helped me with revising the thesis text and provided the 
	laboratory equipment to perform user testing and validation.

	I am grateful for the initial help given by Ing. Tomáš Beneš, 
	for consulting the work's hardware aspects, and for 
	providing me with the equipment used for analysis.

	Finally, my sincere thanks go to everyone closest to me,
	for providing me with encouragement and moral support.
}
\abstractEN{The thesis describes the process of creating a system used for
	enhancing virtual reality with haptic feedback and other external effects.
	The primary objective is to create an open and easily extendable software
	for controlling multiple IoT devices, which works together 
	to provide virtual reality users with effects synchronized with the
	virtual world. The results also include software tools 
	for developers, which allows them to create more immersive 
	and believable virtual reality experiences. 
}
\abstractCS{
	Diplomová práce popisuje proces tvorby systému pro obohacení virtuální
	reality hmatovou zpětnou vazbou a jinými externími efekty. Za primární cíl
	si klade vytvořit otevřený a snadno rozšířitelný software pro ovládání
	vícera IoT zařízení, které společně poskytují uživatelům virtuální reality
	efekty synchronizované s virtuálními světy. Výsledek práce zahrnuje i
	softwarové nástroje pro vývojáře, které jim umožňují vytvořit více
	pohlcující a uvěřitelné zážitky ve virtuální realitě.
}
\placeForDeclarationOfAuthenticity{Prague}
\keywordsCS{virtuální realita, internet of things, webové technologie, Unity Engine}
\keywordsEN{virtual reality, internet of things, web technologies, Unity Engine}
\declarationOfAuthenticityOption{1}
\website{https://github.com/mmajko/openhvr}


\begin{document}

\setsecnumdepth{part}
\input{chapters/01-introduction}

\setsecnumdepth{all}
\input{chapters/02-virtual-reality}
\input{chapters/03-current-state-of-effects}
\input{chapters/04-existing-solutions}
\input{chapters/05-analysis}
\input{chapters/06-proof-of-concept}
\input{chapters/07-design}
\input{chapters/08-implementation}
\input{chapters/09-example-app}
\input{chapters/10-user-testing}

\setsecnumdepth{part}
\input{chapters/11-conclusion}
\input{chapters/12-future-works}
\input{chapters/13-install-guide}
\input{chapters/14-developer-guide}


\bibliographystyle{template/iso690}
\bibliography{bibliography}

\setsecnumdepth{all}
\appendix

\input{appendices/measurements.tex}
\input{appendices/acronyms.tex}
\input{appendices/cd-contents.tex}

\cleardoublepage
\listoffigures

\cleardoublepage
\listoftablescond

\end{document}
